A Simple Type Theory for Category Theory

### 2022-03-15 paper/paper.tex
fix the fibrations

Using the graph of a profunctor, we can give the following definition
for when a functor is a fibration. This gives a very weak notion of
fibration that is probably equivalent to a Street fibration (todo: is
this an existing definition???).

\begin{definition}{Street Fibration}
  Let $F : \varr{\cat C}{\cat D}$, we say $F$ is a \emph{fibration}
  when the induced functor
  \[p : \exists {\alpha:\cat C;\alpha':\cat C} \punitinXfromYtoZ {\cat C}{\alpha}{\alpha'} \vdash (F\pi_-p,F_1\pi_pp, \pi_+p) : \exists {\beta:\cat D;\alpha':\cat C}. \punitinXfromYtoZ {\cat D} \beta {F \alpha'} \]
  has a right adjoint inverse.

  Dually, $F$ is an \emph{op-fibration} when the same induced functor
  has a left adjoint inverse.
\end{definition}

We can get a strict notion of fibration if we allow ourselves to be a little ``evil'':

\begin{definition}{Grothendieck Fibration}
  Let $F : \varr{\cat C}{\cat D}$, we say $F$ is a \emph{strict
  fibration} when the induced functor $F'$ has a strict right adjoint
  inverse $R$, i.e. inverse $\lambda p. R(F'(p)) = \lambda p. p$. We
  analogously define a strict op-fibration.  
\end{definition}

Alternatively, we can give a more traditional definition using slice
categories, but the downside is the formulation is inevitably higher
order.
\begin{definition}{Street Fibration}
  Let $F : \varr{\cat C}{\cat D}$, we say $F$ is a \emph{fibration}
  when for every $a : \varr{1}{\cat C}$, the induced functor
  \[p : \exists {\alpha:\cat C; o:\cat 1} \punitinXfromYtoZ {\cat C}{\alpha}{a()} \vdash (F\pi_-p,F_1\pi_pp, \pi_+p) : \exists {\beta:\cat D; o:\cat 1}. \punitinXfromYtoZ {\cat D} \beta {F(a())} \]
  has a right adjoint inverse.

  Dually, $F$ is an \emph{op-fibration} when the same induced functor
  has a left adjoint inverse.
\end{definition}

@@

>>>>

A (Street) fibration can be defined in any 2-category. A functor $p :
\varr {\cat E}{\cat B}$ is a fibration when the morphism $p \to \cat
B/p$ in the slice 2-category over $\cat B$ has a right adjoint.

Since we can define all of the components of this slice 2-category we
can internalize this definition in SCT.

\begin{enumerate}
\item A functor $\textrm{wp} : \exists (\alpha:\cat B; \beta:\cat E). \punitinXfromYtoZ {\cat B} \alpha {p\beta}$
\item In the slice category: $p(\textrm{wp}(k)) = \pi_-k$
\item With a universal morphism $\epsilon : \pforallXfromYtoZ {k} \punitinXfromYtoZ {} {(\pi_-k,k,\punitrefl{}{\pi_-k})} {k}$
\item In the slice category: $\pi_k \epsilon = \id$ (how to express this nicely in SCT?)
\end{enumerate}

We can also weaken this to a Street fibration if we require the more sensible $p(\textrm{wp}(k)) \cong \pi_-k$ only.

@@

\begin{lemma}{Fibrations are Stable under Pullback}

\end{lemma}
